---
title: "lab-07-simpsons.Rmd"
author: "Refan Nayef AL shammari"
date: "19 March 2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
?Whickham
```
    
Your answer:The data observational as the description states that is based on age, and mortality which are all observable events and not produced via experiments

2.  
```{r observations}
nrow(Whickham) 
```

Your answer;the are 1,314 observations. As we know every row is observation

3.  

```{r number_variables}
names(Whickham) 
```

Your answer:There are 3 variables, "outcom" , "smoker", and "age"  

```{r var_type}
unique(Whickham$outcome)
unique(Whickham$smoker) 
unique(Whickham$age)

```

Your answer: Using the 'unique()' function on the 3 variables we could see that "outcome" only takes Alive or Dedd valiue, which makes it categorical non-ordinal. "smoker" only takes Yes or No, which also makes it categorical non-ordinal. Age is numerical continous data

On of the best ways to visualise categorical data is through the use of bar charts
```{r plot_outcome}
ggplot(Whickham, aes(x = outcome)) +
  geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x = smoker)) +
  geom_bar() 
```

```{r plot_age}
ggplot(Whickham, aes(x = age)) +
  geom_boxplot()
```


4. 

```{r plot_smokeVSincome_1}

```

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```

6.

```{r age_cat}

```

7. 

```{r plot_smokeVSincome_3}

```

Knit, commit, and push to github.